Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-13 sections/correlated-sicm-and-fm.tex
Added the Gorelik-reserch to the widefield-FM part

\section{Correlating SICM and Fluorescence Microscopy}
\label{sec:correlating-sicm-and-fm}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../manuscript"
%%% End:

@@

% Den folgenden Teil verstehe ich nicht wirklich, SICM kann ja auch 3D
% (allerdings natürlich nicht innerhalb von irgendetwas). Und irgendwie ist
% das ja auch nicht der "Haupt"-Vorteil, sondern, dass man überhaupt
% Fluoreszenz sehen kann.

% This is especially helpful for applications, where the reaction is not limited to \emph{one 
% dimension}, for example when investigating the uptake of nanoparticles into cells. There it would 
% be interesting to investigate, sowohl %german
% the cell membrane with a technique, which is able to do so -- AFM \cite{}, EM \cite{}, SICM 
% \cite{Hansma1989} --, als auch %german
% to follow the nanoparticle into the cell or to investigate simultaneously how the cytoskeleton 
% react on the addition (?) of the nanoparticle by using fluorescence microscopy methods.

% % Den Teil brauchen wir ja vielleicht nicht. 
% AFM, a method belonging to the scanning probe microscopy techniques, was successfully
% combined to fluorescence microscopy techniques e.g. to investigate the topography of a 
% cell or a part of a cell with the cytoskeleton \cite{Laishram2009,Liu2020}. But a big problem 
% with this method is, that it is not the most favorable for investigating living cells in their
% physiological surrounding. Certain destructive effects on the cell were found by using this 
% technique \cite{}. A better fitting method for investigating living cells would be scanning 
% ion conductance microscopy (SICM) \cite{Hansma1989}.

% Hier jetzt der surface confocal scanning part, NP investigation part usw. (damit warte ich aber,
% bis ich weiß, wie das richtig eingefügt wird.

% Another very delicate sample, because of their three-dimensional, upright structure are cilia.
% Here SICM was used for investigating the topography of the cilia and the fluorescence was used to
% distinguish between surface and sub-surface cilia, which could not be detected with SICM 
% \cite{Zhou2018}.
\subsection{Combining SICM and confocal FM}

@@

SSCM has been used for investigating the dynamics of the interaction of
Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells
(Fig.~\ref{fig:sicm+scm}b,d) \cite{Gorelik2002a}, for the investigation of the
uptake of fluorescent nanoparticles in immortalized human alveolar epithelial
type 1 (AT1) cells and AT2 cells \cite{Kemp2008,Novak2014} and for investigating the
differentiation of stem cells \cite{Gorelik2008}. Furthermore, it has been
utilized in studies investigating endocytotic pathways \cite{Shevchuk2008}
(Fig.~\ref{fig:sicm+scm}c) and in a study revealing an alternative closing
mechanism for clathrin-coated pits by recording topography simultaneously with
the fluorescence of tagged actin-binding protein and the tagged
clathrin light-chain \cite{Shevchuk2012}.

%Anmerkung: Habe die folgenden Paragraphen versucht in oberen Text einzubauen und deshalb hier 
%auskommentiert.

%Scanning surface confocal microscopy (SSCM) was a combination of scanning ion conductance and a 
%scanning confocal microscopy \cite{Gorelik2002}. The topography and fluorescence were measured
%simultaneously and -- because fluorescence signals should be investigated, which were originated
%from particles at or near to the surface of the cell -- it was important to keep the distance 
%between the sample and the pipette constant. In that study the SSCM was used for investigating the 
%dynamics of the interaction of Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells. 
%The SSCM could also be used for the investigation of the uptake of fluorescent nanoparticles 
%(50~nm and 1~{\textmu}m) in immortalized human alveolar epithelial type 1 (AT1) cells and AT2 
%cells \cite{Kemp2008} or for investigating the differentiation of stem cells \cite{Gorelik2008}.
%
%SSCM could be also used for investigating endocytotic pathways \cite{Shevchuk2008}. In a study 
%investigating topography together with actin-binding protein-green fluorescent protein (Abp1-GFP)
%and clathrin light-chain-enhanced green fluorescent protein (Clc-EGFP) an alternative closing 
%mechanism for clathrin-coated pits (CCPs) \cite{Shevchuk2012}. In another study the uptake of
%200~nm fluorescent, carboxylated latex particles into immortalized human alveolar epithelial type
%1-like (AT1) cells was investigated. Additional to the fluorescence signal of the nanoparticle the 
%fluorescence signal of actin-binding protein-green fluorescent protein (Abp1-GFP) and clathrin
%light-chain-enhanced green fluorescent protein (Clc-EGFP) were detected. Both, actin, as part of
%the cytoskeleton (Quelle), and clathrin, as one important actor of endocytosis (Quelle), give 
%interesting Zusatzinformationen on how the nanoparticle is taken up into the cell 
%\cite{Novak2014}.

@@

SICM in combination with Förster resonance energy transfer (FRET) sensors could be used for
the localisation of $\beta_{1}$-adrenoceptors \cite{Wright2018}, $\beta_{2}$-adrenoceptors 
\cite{Nikolaev2010,Lyon2012,Wright2014,Wright2018} and $\beta_{3}$-adrenoceptors 
\cite{Schobesberger2020} in healthy and impaired cardiomyocytes \cite{Wright2015,Berisha2017}. 
After measuring the topography (SICM) the nanopipette could be moved to places -- e.g. the 
z-grooves of the cell \cite{Gorelik2006,Lyon2009,Miragoli2011,Lyon2012,Rivaud2017} -- where the 
adrenoceptor distribution should be investigated. Then the pipette could be used for stimulating 
the receptor to produce cyclic adenosine monophosphate (cAMP) or cyclic guanosine monophosphate 
(cGMP) \cite{Xiang2003}, this could bind to the FRET sensor (in the cell), which changes its 
conformation and a FRET signal could be detected \cite{Nikolaev2010}.

>>>>

\section{Correlating SICM and Fluorescence Microscopy}
\label{sec:correlating-sicm-and-fm}

@@

\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/Nikolaev2010-F2}
  \caption{
    \textbf{a:}\textbf{b:}\textbf{c:}\textbf{d:}\textbf{e:}\textbf{f:}
  }
  \label{fig:nikolaev2010}
\end{figure}
Cardio-myocytes exhibit a unique topography with transverse (T-)tubules and
crests (Fig.~\ref{fig:nikolaev2010}a, b). By first recording the topography
and subsequently moving the SICM pipette to either a T-tubule or a crest,
followed by the local application of agonists of either the $\beta_1$- or
$\beta_2$-adrenergic receptor (AR) and recording the intensity ratio of cyan
and yellow fluorescent protein, coupled to a Förster resonance energy transfer
(FRET) based reporter of cyclic AMP (Fig.~\ref{fig:nikolaev2010}c--f), it was
shown that the distribution of the $\beta_2$-AR was altered in failing
cardio-myocytes \cite{Nikolaev2010}. Furthermore, this approach was used to
investigate the effect of partial mechanical unloading, showing that it
reduces the cyclic AMP response of $\beta_2$-ARs at the T-tubules
\cite{Wright2018}. To investigate the distribution of the $\beta_3$-AR, the
approach was extended to use a FRET-based reporter of cyclic GMP, showing that
a redistribution of the $\beta_3$-AR occurs in failing cardio-myocytes, too
\cite{Schobesberger2020}.

\subsection{Combining SICM and confocal FM}

@@

SSCM has been used for investigating the dynamics of the interaction of
Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells
(Fig.~\ref{fig:sicm+scm}b,d) \cite{Gorelik2002a}, for the investigation of the
uptake of fluorescent nanoparticles in immortalized human alveolar epithelial
type 1 (AT1) cells and AT2 cells \cite{Kemp2008,Novak2014} and for investigating the
differentiation of stem cells \cite{Gorelik2008}. Furthermore, it has been
utilized in studies investigating endocytotic pathways \cite{Shevchuk2008}
(Fig.~\ref{fig:sicm+scm}c) and in a study revealing an alternative closing
mechanism for clathrin-coated pits by recording topography simultaneously with
the fluorescence of tagged actin-binding protein and the tagged
clathrin light-chain \cite{Shevchuk2012}. A further study on clathrin-coated
pit formation and maturation revealed the effect of mutations in the Dynamin~2
gene on the maturation and internalisation of clathrin coated pits \cite{Ali2019}.

@@
